Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-02-10 paper/ms.tex
Add lsr to paper in Appendix

\subsection{Local Midplane} \label{sec:local_midplane}
We now turn to defining the local midplane that an observer might measure if
they were situated in each of these galaxies. We place our imaginary observer
at the solar radius of $8.2\,\kpc$ and azimuth $\phi$\footnote{Our erroneous,
immortal observer is also warp-drive capable.}, and consider stars within a
cylinder of radius $0.5\,\kpc$ and height $1\,\kpc$ perpendicular to the
fiducial disk.

@@

>>>>

\subsection{Local Midplane} \label{ssec:local_midplane}
We now turn to defining the local midplane that an observer might measure if
they were situated in each of these galaxies. We place our imaginary observer
at the solar radius of $8.2\,\kpc$ and azimuth $\phi$\footnote{Our erroneous,
immortal observer is also warp-drive capable.}, and consider stars within a
cylinder of radius $0.5\,\kpc$ and height $1\,\kpc$ perpendicular to the
fiducial disk.

@@

\section{LSR Variations} \label{app:lsr}
\begin{figure*}
\plotone{fig/lsr.pdf}
\caption{The local standard of rest (LSR) as a function of azimuth at the
fiducial Solar circle ($R_{\odot} = 8.2\,\kpc$). No best-fit subtraction is
performed here as we did in the case of the midplane
(Section~\ref{ssec:local_midplane}).}
\end{figure*}
